Union and intersection contracts are hard, actually

### 2021-09-15 paper.tex
Update paper.tex
Co-authored-by: Arnaud Spiwack <arnaud.spiwack@tweag.io>

Strikingly, we will see in Section~\ref{sec:issues-sem} that the introduction of
union and intersection contracts \emph{breaks referential transparency} and make
(\ref{eq:cbn-expansion}) \emph{unsound}\footnote{(\ref{eq:cbn-expansion}) holds
  even in a technically impure language like Nickel with non-termination and
  higher-order contracts because of lazy evaluation. This is not the case in a strict language,
  although in that case, (\ref{eq:cbn-expansion}) still holds more often without
  unions and intersections than with.}, preventing the kind of optimization of
Figure~\ref{fig:optimizations-let-floating-ex} to fire in general.

>>>>

Strikingly, we will see in Section~\ref{sec:issues-sem} that the introduction of
union and intersection contracts \emph{breaks referential transparency} and make
(\ref{eq:cbn-expansion}) \emph{unsound}\footnote{(\ref{eq:cbn-expansion}) holds
  in Nickel despite non-termination and contract-checking errors
  because of lazy evaluation. In strict languages (\ref{eq:cbn-expansion}) needs to be restricted, nevertheless
  union and intersection contracts make it worse.}, preventing the kind of optimization of
Figure~\ref{fig:optimizations-let-floating-ex} to fire in general.
